On Secure Delegation of SampBQP with a Classical Client

### 2019-12-27 introduction.tex
Add notes about intro

Below is some intro of it copied from my SoP.
This is unpolished and mostly a placeholder at the moment though.

@@

\hannote{paste}

>>>>

\Ethan{This section is currently all rough draft. We'll probably rewrite almost all of it.}

\Ethan{Below is my attempt to talk about it in my SoP}

@@

\Ethan{Below is my attempt to talk about it in my research proposal}
